### 2015-11-16 postdoctoral/S_prime_kappa.tex
Add alan's result and some gamma function stuff shoot I meant to do separate commits

@@

  \begin{theorem}
    There's a model where \(S'(\omega_\omega)\)
    fails? (TODO: get Alan to send this argument.)
  \end{theorem}

@@

\end{document}

>>>>

% dow stuff
          \def\Succ{\mathop{Succ}}
          \def\dom{\mathop{dom}}
          \def\val{\operatorname{val}}
          \def\N{\mathbb N}
          \def\Nstar{\mathbb N^*}

@@

  \begin{theorem}
    There's a model where \(S'(\omega_\omega)\)
    fails.
  \end{theorem}

  \begin{proof}
          We will need the model constructed in \cite{MR1045371} in
           which an instance of Chang's conjecture
           $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
           (\aleph_1,\aleph_0)$ is shown to fail.

          We can take as a given (as shown in \cite[Theorem 5]{MR1045371}) that we may
          assume that we have a model $V$
          of GCH in which there are regular limit cardinals $\kappa<\lambda$
          satisfying that
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$.

          What this says is that if $L$ is a countable language
          with at least one unary relation symbol $R$ and
           $M$ is a model of $L$  with base set $\lambda^{+\omega+1}$
          in which the interpretation of $R$ has cardinality
           $\lambda^{+\omega}$, then $M$ has an elementary submodel
           $N$ of cardinality $\kappa^{+\omega+1}$ in which
          $R\cap N$ has cardinality $\kappa^{+\omega}$ (of course
           $R\cap N$ is the interpretation of $R$ in $N$ because
          $N\prec M$).

          The interested reader will want to know that it is shown in
          \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal and $j$ is the 2-huge
          embedding with critical point $\kappa$, then with
           $\lambda = j(\kappa)$ one has that
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$ holds.
          \bigskip

          Let $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$
          be a scale in $\Pi\{ \lambda^{+n+1} : n\in \omega\}$
           ordered by the usual mod finite coordinatewise
          ordering. For convenience we may assume that $h_\xi(n) \geq
          \lambda^{+n}$ for all $\xi$ and all $n$.  If $P$ is any poset of
          cardinality less than $\lambda^{+\omega}$, then in the forcing
          extension by $P$,  the sequence
          $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$  remains cofinal in
           $\Pi\{ \lambda^{+n+1} : n\in \omega\}$.

          The forcing notion $\mathbb P_0$ is simply the finite condition
          collapse of $\kappa^{+\omega}$, i.e. $\mathbb P_0 = \left(
           \kappa^{+\omega}\right)^{<\omega}$. In the forcing extension by
           $\mathbb P_0$, one now has that the ordinal $\kappa^{+\omega+1}$
           from $V$ is the first uncountable cardinal $\aleph_1$. Then in this
           forcing extension we let $\mathbb P_1$ be the countable condition
           Levy collapse, $Lv(\lambda,\omega_2)$, which collapses all cardinals
           less than $\lambda$ to have cardinality at most $\aleph_1$. The poset
           $\mathbb P_1$ has cardinality $\lambda$. We treat
          $\mathbb P_1$ as containing $\mathbb P_0$
          as a subposet by identifying each $(p_0,1)$ with $p_0$.
          After forcing with $\mathbb P_0*\mathbb P_1$ we will have
          that $\omega_1$ is the ordinal $\left(\kappa^{+\omega+1}\right)^V$,
           $\omega_2$ is the ordinal $\lambda$, and $\omega_\omega$ is the
           ordinal $\left(\lambda^{+\omega}\right)^V$.

          Now we assume that we have an assignment $\dot f_{\dot A}$ of a
           $\mathbb P_0*\mathbb P_1$-name of a finite-to-one function from
           $\dot A$ into $\omega$ for each
           $\mathbb P_0*\mathbb P_1$-name of a countable subset of
           $\lambda^{+\omega+1}$. We will obtain a contradiction.

          Let $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$ be an enumeration
          of all the  nice $\mathbb P_0$-names of countable
          subsets of $\lambda^{+\omega}$. For each $\xi\in \lambda^{+\omega+1}$,
           let $\dot f_\xi$ be another notation for $\dot f_{\dot A_\xi}$.
          Since $\mathbb P_0$ forces that $\mathbb P_1$ is countably closed,
          the collection of all nice  $\mathbb P_0$-names will produce all
          the countable sets in the extension by $\mathbb P_0* \mathbb
          P_1$, but $\mathbb P_0*\mathbb P_1$ can introduce new enumerations of
          these names.
          For each $\xi\in \lambda^{+\omega+1}$,
          there is a minimal $\zeta_\xi$ so that $\dot A_{\zeta_\xi}$ is the
          canonical name for the range of $h_\xi$. This means that
           $\dot f_{\zeta_\xi} \circ h_\xi$ is simply the
           $\mathbb P_0 *\mathbb P_1$-name of a finite-to-one function from
           $\omega$ to $\omega$.
            For each $\xi\in \lambda^{+\omega+1}$,
           choose any $p_\xi \in \mathbb P_0*\mathbb P_1$ so that
           there is a nice $\mathbb P_0$-name, $\dot H_\xi$,
           that is forced by
           $p_\xi$  to equal $\dot f_{\zeta_\xi}\circ h_\xi$.
            Choose $\Lambda\subset \lambda^{+\omega+1}$
            of cardinality $\lambda^{+\omega+1}$
            and so that there is a pair $p,\dot H$
            satisfying that $p_\xi = p$ and $\dot H_\xi = \dot H$
            for all $\xi\in \Lambda$. We may assume that $p$
            is in a generic filter $  G$.

          Let $\{ x_\xi : \xi\in \lambda^{+\omega+1}\}$ be any enumeration of
           $H(\lambda^{+\omega+1})$  such that
           $\{ x_\xi : \xi\in \lambda^{+\omega}\}$ is also equal to
           $H(\lambda^{+\omega})$. We choose this enumeration in such a way that
           $x_\xi\in x_\eta$ implies $\xi<\eta$.
          We use relation symbol $R_0$ to code
          (and well order)
           $(H(\lambda^{+\omega+1}), \in)$ as follows: $(\xi,\eta)\in R_0$
          if and only if $x_\xi\in x_\eta$.
          Let $R_1$ be a binary relation on $\kappa^{+\omega}$ so that
          $(\kappa^{+\omega},R_1)$ is isomorphic to $\mathbb P_0$. Let
           $R_2$ be a binary relation on $\lambda$ so that
           $R_2\cap (\kappa^{+\omega}\times \kappa^{+\omega})=R_1$ and
           $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
          Let $\psi$ be the poset isomorphism from $\lambda$ to
           $\mathbb P_0*\mathbb P_1$.

          We continue coding. We can code the sequence
           $\{ h_\xi : \xi\in \lambda^{+\omega+1}\}$ as another binary  relation
           $R_3$ on $\lambda^{+\omega+1}$ where $R_3\cap \left(\{\xi\}\times
           \lambda^{+\omega+1}\right) = \{ (\xi,h_\xi(n) ) : n\in \omega\}$
          for each $\xi\in \lambda^{+\omega+1}$. The relation symbol $R_4$ can
          code the sequence $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$
          where $(\xi, \alpha, \zeta) \in R_4$ if and only if
          $(\check \alpha, \psi(\zeta))$ is in the name $\dot A_\xi$.
           Let $R_5$ code this collection, i.e.
           $(\gamma,n,m,\eta)\in R_5$ if and only if
           $(\check{(n,m)}, \psi(\eta))\in \dot H_\gamma$. Also let $R_6$ code
           (equal)  the set $\Lambda$.
          Finally we use the relation symbol $R_7$ to similarly code the
          sequence $\{ \dot f_\xi  : \xi \in \lambda^{+\omega+1}\}$:
           $(\xi, \alpha, n, \zeta) \in R_7$ if and only if
          $(\check {(\alpha,n)}, \psi(\zeta))$ is in the name $\dot f_\xi$.

          Needless to say, the unary relation symbol $R$
          is interpreted as the set $\lambda^{+\omega}$ for the application of
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$.
           Now  we have defined our model
          $M$  of the language $L= \{\in, R, R_0,\ldots, R_7\}$,
           and we choose an elementary submodel
          $N$ witnessing
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$. Of course $N$ is really just
          a $\kappa^{+\omega+1}$ sized subset of $\lambda^{+\omega+1}$
          with the additional property that $N\cap \lambda^{+\omega}$ has
          cardinality $\kappa^{+\omega}$.  In the
          forcing extension $N$ has cardinality $\omega_1$ and
           $A= N\cap \lambda^{+\omega}$ is countable.

          We will need the following claim from \cite{MR1045371}

          \begin{claim*} We may assume that $N$ satisfies that
           $N\cap \kappa^{+\omega+1}$ is transitive (i.e. an initial segment).
          \end{claim*}

          \begin{proof}[Proof of Claim]
          Suppose  our originally supplied $N$ fails the conclusion of the
          claim.
          We   know that $\kappa^{+\omega}\in N$,
          (  via $R_1$)
          in which case so is $\kappa^{+\omega+1}$.

          Then set $\beta_0 = \sup(N\cap \kappa^{+\omega+1})$ and consider the
          Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
          (in that we have to formalize the enumeration of formulas)
          let $\{\varphi_n : n\in \omega\}$ is the enumeration of all formulas
          in the language $L$, and let  $\ell_n$ be the minimal integer such
          that the free variables of $\varphi_n$ are among
           $\{ v_0, \ldots, v_{\ell_n}\}$.
          Then,   for each tuple
          $\langle \xi_1,\ldots, \xi_{\ell_n} \rangle$
          of elements of $\lambda^{+\omega+1}$,
           we define $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be
           the minimal $\xi_0\in \lambda^{+\omega+1}$ such that
           $M\models \varphi_n(\xi_0,\ldots, \xi_{\ell_n})$.
          If there is no such $\xi_0$,
             in other words if $M\models \lnot\exists x~~  \varphi_n(x,\xi_1,
          \ldots,\xi_{\ell_n})$, then set
           $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be $0$.
          Now $\mathop{Hull}(N\cup \beta_0,M)$ is just the minimal superset
           $X$
          of $N\cup \beta_0$ that satisfies that
           $f_n[X^{\{1,\ldots,\ell_n\}}] \subset X$ for all $n$. Since this is
           simply a large algebra, we can generate all the terms $t$ of
          the algebraic operations $\{ f_n : n\in \omega\}$.
          It is easily seen that for each $\zeta \in X$, there is a term
          $t(v_1,\ldots, v_m)$ such that $\zeta  = t(\delta_1,\ldots, \delta_m)$
           for some sequence $\langle \delta_1,\ldots, \delta_m\rangle$ with
           each $\delta_i\in  N\cup \beta_0$.
           Assume that
            $\zeta\in \kappa^{+\omega+1}$. By
            re-indexing the variables in the term we can assume
            that there is an $n\leq m$ so that
             $\delta_i  <\beta_0$ for $1\leq i\leq n$
              and $\kappa^{+\omega+1}\leq \delta_i$ for $n<i\leq m$.
              Let $\vec a $ denote
              the tuple $\langle \delta_{n+1},\ldots, \delta_m\rangle$.
            Choose $\eta\in N\cap \kappa^{+\omega+1}$ large enough so that
           $ \{  \delta_1, \ldots, \delta_n\}$ is contained in  $\eta$. Since set-membership
           in $M$ is coded by $R_0$ rather than $\in$ we have to argue a little
           less naturally.
           Consider the set
             $s_0(\eta,\vec a) = \{ t(\gamma_1,\ldots, \gamma_n,\vec a) :
          \{\gamma_1,\cdots,\gamma_n\} \in [\eta]^{\leq n}\}$. Clearly
           $s_0(\eta,\vec a)$ is a member of $H(\lambda^{+\omega+1})$.
           Now define $s_1(\eta,\vec a) $ to be
           $\{ x_\alpha : \alpha\in s_0(\eta, \vec a)\}$,
           and choose the
           unique $\zeta_1\in \lambda^{+\omega+1}$ such
           that $x_{\zeta_1} = s_1(\eta,\vec a)$. We claim that $\zeta_1\in N$.
           Note that $\alpha R_0\zeta_1$ holds if and only if
            $ \alpha \in s_0(\eta,\vec a)$, and therefore
           $$M\models (\forall \alpha)\left[\alpha R_0 \zeta_1 ~~\mbox{iff}~~
           (\exists   \gamma_1\in \eta)\cdots(\exists \gamma_n\in\eta)(\alpha=
           t(\gamma_1,\ldots, \gamma_n,\vec a))\right]~.$$
           By elementarity then we have that $\zeta_1\in N$,
           and by similar reasoning the supremum, $\zeta_0$,
          of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
             This of course means that $\zeta < \xi_0$.
          \end{proof}

          We use the elementarity of
           $N$  to deduce properties of the families
           $\{ \dot A_\xi : \xi\in N\}$ and $\{ \dot f_\xi : \xi \in
           N\}$.  Actually the collection we are most interested in
           is the family $\{ h_\xi : \xi\in \Lambda\cap N\}$.

           Since  $\mathfrak c < \kappa^{+\omega+1}$ there
            is a function $\langle \varrho_n : n\in \omega\rangle$
            in $\Pi_n \lambda^{+\omega}   $ such that the sequence
             $\{ h_\xi : \xi \in N\}$ is unbounded mod finite
             in $\Pi_n \varrho_n$ (by Shelah's pcf theory).
             This is in Jech somewhere.
             For each $n$, $\rho_n \leq \sup(N\cap \lambda^{+n+2})$.

             Since $\mathbb P_0$ has cardinality less than $|N|=\kappa^{+\omega+1}$,
              the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains unbounded
              mod finite in $\Pi_n \varrho_n$ (and in
               $\Pi_n (\varrho_n\cap N)$).  Now pass to the extension by
                $G\cap \mathbb P_0$ and let $H$ be the function
                 $\operatorname{val}_{G}(\dot H)$, and we recall
                 that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$.
           Now pass to the full extension $V[G]$ and again, since
            $\mathbb P_1$ was forced to be countably closed,
             the family $\{ h_\xi : \xi \in \Lambda\cap N\}$ is still
             unbounded in $\Pi_n (\varrho_n \cap N)$. We let
             $A$ be the countable set $N\cap \lambda^{+\omega}$,
             and for  each
             $\xi\in \Lambda\cap N$, there is an $n_\xi$ such that
              $f_{\xi}(h_\xi(m)) = f_A(h_\xi(m))$ for all $m>n_\xi$.
              There is a single $n$ so that $\Lambda_n
               = \{\xi\in \Lambda\cap N       : n_\xi = n\}$ has cardinality
                $\omega_1 $, and thus
                $\{ h_\xi : \xi\in \Lambda_n\cap N\}$ is also unbounded
                in $\Pi_n (\rho_n\cap N)$.
          This certainly implies that there is an $m>n$
          such that $\{ h_\xi (m) : \xi\in \Lambda_n\cap N\}$ is infinite.
          This completes the proof since  $f_{A}(h_\xi(m)) = H(m)$
          for all $\xi\in \Lambda_n\cap N$.

@@

\newpage
\bibliographystyle{plain}
\bibliography{../bibliography}
\end{document}

### 2015-11-16 postdoctoral/gamma_functions.tex
Add alan's result and some gamma function stuff shoot I meant to do separate commits

  \begin{definition}
    For any compact LOTS \(K\) with minimum \(0\) and maximum \(1\),
    let \(\gamma\) be the V-map on \(K\) where \(\gamma(0)=K\) and \(\gamma(t)=\{1\}\)
    for \(t>0\).
  \end{definition}

@@

  We may generalize theorem 8 as follows:

  \begin{theorem}
    If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

@@

>>>>

  \begin{definition}
    For any space \(M\) containing the points \(0\) and \(1\),
    let \(\gamma\) be the surjective u.s.c. map on \(K\) where
    \(\gamma(0)=M\) and \(\gamma(t)=\{1\}\)
    for \(t\not=0\).
  \end{definition}

  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a V-map.
  It's usually assumed \(0\) is the minimum and \(1\) is the maximum
  when \(M\) is a LOTS.

@@

  We may generalize theorem whatevs as follows:

  \begin{theorem} %TODO fix first \sim to use A,B instead of l_0,l_1
    If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

@@

  We now discard the linear order on \(M\). Denote points in the topological
  sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
  by the ordered pairs \(\<A,m\>\)
  for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
  show the following:

  \begin{theorem}
    If \(M\) is a Hausdorff space with points \(0\) and \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

  % \begin{proof}
  %   Partially order \(M\) by \(0\leq m\leq 1\) for all \(m\in M\).
  %   Note that the range of any
  %   \(\vect x\in\varprojlim\{M,\gamma,L\}\) is totally ordered by \(\leq\).

  %   Let \(\rho(\vect x)=\cl\{l\in L:\vect x(l)>0\}\), \(v(\vect 0)=0\),
  %   and \(v(\vect x)=\min\{\vect x(l):l\in\rho(\vect x)\}\) otherwise.
  %   Let
  %   \(\theta(\vect x)=\<\rho(\vect x),v(\vect x)\>\in\hat L\lexTimes M/\sim\).
  %   For each left-closed set \(A\) and \(m\in M\),
  %   let \(\vect x_{A,m}(l)=1\) for \(l\in A\) unless \(l\) is the supremum
  %   element of \(A\),
  %   \(\vect x_{A,m}(l)=m\) if \(l\) is the supremum of \(A\),
  %   and \(\vect x_{A,m}(l)=0\) for \(l\not\in A\).
  %   We wish to show that \(\theta\) is a homeomorphism.

  %   We begin by
  %   showing that \(\theta\) is a surjection. If \(B\in\hat L\setminus L\)
  %   and \(m\in M\), consider \(\<B,m\>\).
  %   \(B\) lacks a supremum in \(L\), so
  %   \(\vect x_{B,0}(l)=1\) for \(l\in B\) and \(\vect x_{B,0}(l)=0\) otherwise.
  %   So \(\theta(\vect x_{B,0})=\<\cl B,1\>=\<B,1\>\sim\<B,m\>\) for all
  %   \(m\in M\). Otherwise, \(B=(\leftarrow,l_1]\) for some \(l_1\in L\).
  %   Let \(m>0\).
  %   Then
  %   \(
  %     \theta(\vect x_{(\leftarrow,l_1],m})
  %       =
  %     \<\cl (\leftarrow,l_1],v(\vect x_{(\leftarrow,l_1],m})\>
  %       =
  %     \<(\leftarrow,l_1],m\>
  %   \).
  %   Finally, we want to map onto \(\<(\leftarrow,l_1],0\>\).
  %   If there exists \(l_0<l_1\) with \((l_0,l_1)=\emptyset\), then
  %   \(
  %     \theta(\vect x_{(\leftarrow,l_1],0})
  %       =
  %     \theta(\vect x_{(\leftarrow,l_0],1})
  %       =
  %     \<(\leftarrow,l_0],1\>
  %   \)
  %   will suffice. Otherwise,
  %   \(
  %     \theta(\vect x_{(\leftarrow,l_1],0})
  %       =
  %     \<\cl (\leftarrow,l_1),v(\vect x_{(\leftarrow,l_1),0})\>
  %       =
  %     \<(\leftarrow,l_1],0\>
  %   \).

  %   To see that \(\theta\) is injective, first let
  %   \(A\subsetneq B\)... TODO

  %   % A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
  %   % is of the form
  %   % \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
  %   % \(l\in F\in [L]^{<\omega}\), and
  %   % \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
  %   % If we assume that \(\lb U,F \rb\) is non-empty, one of the following
  %   % must hold:

  %   % \begin{itemize}
  %   %   \item
  %   %     \(U[l_0]=(a,b)\) for some \(l_0\in F\).
  %   %     Then \(\lb U,F\rb=\lb U,\{l_0\}\rb \), and note that
  %   %     \(
  %   %       \lb U,\{l_0\}\rb
  %   %         =
  %   %       (\vect x_{(\leftarrow,l_0],a},\vect x_{(\leftarrow,l_0],b})
  %   %     \).
  %   %   \item
  %   %     \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
  %   %     and \(\lb U,F\rb=\lb U,\{l_0,l_1\}\rb \). Then
  %   %     \(\lb U,\{l_0,l_1\}\rb =(\vect x_{l_0,a},\vect x_{l_1,b})\).
  %   % \end{itemize}
  %   % In the other direction, consider \(\vect y\in(\vect x,\vect z)\).
  %   % \begin{itemize}
  %   %   \item
  %   %     In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\)
  %   %     and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\), let
  %   %     \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
  %   %   \item
  %   %     In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\),
  %   %     \(\rho(\vect y)=\rho(\vect z)\), and \(v(\vect y)<v(\vect z)\),
  %   %     it follows that \(\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_1]\),
  %   %     so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
  %   %   \item
  %   %     In the case that
  %   %     \(\rho(\vect x)=\rho(\vect y)\), \(v(\vect x)<v(\vect y)\),
  %   %     and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\),
  %   %     it follows that \(\rho(\vect x)=\rho(\vect y)=(\leftarrow,l_0]\),
  %   %     so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
  %   %   \item
  %   %     In the case that
  %   %     \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)\) and
  %   %     \(v(\vect x)<v(\vect y)<v(\vect z)\),
  %   %     it follows that
  %   %     \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_0]\),
  %   %     so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
  %   %     \(\vect y\in\lb U,\{l_0\}\rb =(\vect x,\vect z)\).
  %   % \end{itemize}

  %   % We conclude by
  %   % showing that \(\theta\) is a surjection. If \(B\in\hat L\setminus L\)
  %   % and \(m\in M\), consider \(\<B,m\>\).
  %   % \(B\) lacks a supremum in \(L\), so
  %   % \(\vect x_{B,0}(l)=1\) for \(l\in B\) and \(\vect x_{B,0}(l)=0\) otherwise.
  %   % So \(\theta(\vect x_{B,0})=\<\cl B,1\>=\<B,1\>\sim\<B,m\>\) for all
  %   % \(m\in M\). Otherwise, \(B=(\leftarrow,l_1]\) for some \(l_1\in L\).
  %   % Let \(m>0\).
  %   % Then
  %   % \(
  %   %   \theta(\vect x_{(\leftarrow,l_1],m})
  %   %     =
  %   %   \<\cl (\leftarrow,l_1],v(\vect x_{(\leftarrow,l_1],m})\>
  %   %     =
  %   %   \<(\leftarrow,l_1],m\>
  %   % \).
  %   % Finally, we want to map onto \(\<(\leftarrow,l_1],0\>\).
  %   % If there exists \(l_0<l_1\) with \((l_0,l_1)=\emptyset\), then
  %   % \(
  %   %   \theta(\vect x_{(\leftarrow,l_1],0})
  %   %     =
  %   %   \theta(\vect x_{(\leftarrow,l_0],1})
  %   %     =
  %   %   \<(\leftarrow,l_0],1\>
  %   % \)
  %   % will suffice. Otherwise,
  %   % \(
  %   %   \theta(\vect x_{(\leftarrow,l_1],0})
  %   %     =
  %   %   \<\cl (\leftarrow,l_1),v(\vect x_{(\leftarrow,l_1),0})\>
  %   %     =
  %   %   \<(\leftarrow,l_1],0\>
  %   % \).
  % \end{proof}
